How long to simulate?

### 2015-01-22 manuscript.tex
Add cogsci style

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{authblk}
\usepackage{apacite}
\usepackage{color}
\usepackage{setspace}

@@

\doublespacing{}

\title{Making decisions from samples with variable time costs}
\author{Jessica B. Hamrick (\texttt{jhamrick@berkeley.edu})}
\date{}\bibliographystyle{apacite}

@@

@@

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/thresholds.pdf}
        \caption{\textbf{Rates of return and optimal thresholds.} In all plots, each line corresponds to a particular cost ratio, $t_a/t_s$. Black dots in the left two subplots show the optimal threshold $T^*$ and corresponding rate of return for each line. Left subplot: rates of return for a fixed time cost. Middle subplot: rates of return for a variable time cost. The distribution of $t_s$ was calculated empirically from simulations of a ball bouncing in a box (see Section \ref{sec:model}). Right subplot: difference in rates of return between the variable time cost and fixed time cost, approximated with Equation \ref{eq:ror-diff}.}
        \label{fig:rors}
    \end{center}
\end{figure}

@@

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. The left panel shows the initial screen presented to the participant. The middle panel shows the occluded ball, after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. The right panel shows the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure}

@@

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure}

@@

>>>>

\documentclass[10pt,letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}

\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\usepackage{color}

@@

\title{How long to simulate?}

\author{{\large \bf Jessica B.~Hamrick (jhamrick@berkeley.edu)} \\
  Department of Psychology \\
  University of California, Berkeley
  \AND {\large \bf Kevin A.~Smith (k2smith@ucsd.edu)} \\
  Department of Psychology \\
  University of California, San Diego
  \AND {\large \bf Thomas L.~Griffiths (tom\_griffiths@berkeley.edu)} \\
  Department of Psychology \\
  University of California, Berkeley
  \AND {\large \bf Edward Vul (evul@ucsd.edu)} \\
  Department of Psychology \\
  University of California, San Diego}

@@

\begin{abstract}
\TODO{}

\textbf{Keywords:} 
add your choice of indexing terms or keywords; kindly use a
semicolon; between each term
\end{abstract}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/thresholds.pdf}
        \caption{\textbf{Rates of return and optimal thresholds.} In all plots, each line corresponds to a particular cost ratio, $t_a/t_s$. Black dots in the left two subplots show the optimal threshold $T^*$ and corresponding rate of return for each line. Left subplot: rates of return for a fixed time cost. Middle subplot: rates of return for a variable time cost. The distribution of $t_s$ was calculated empirically from simulations of a ball bouncing in a box (see Section \ref{sec:model}). Right subplot: difference in rates of return between the variable time cost and fixed time cost, approximated with Equation \ref{eq:ror-diff}.}
        \label{fig:rors}
    \end{center}
\end{figure*}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. The left panel shows the initial screen presented to the participant. The middle panel shows the occluded ball, after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. The right panel shows the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure*}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

@@

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}
